Hierarchical Dispatching and Overriding

### 2017-09-27 NewVersion/sections/Formalization.tex
refine s3 text

Expressions can be standard constructs such as variables, method
invocation, or object creation. \name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of expressions: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
implementation for method $m$ should be along the path $I$. 
% Another interesting expression are super-invocations, which enable a method to access an old implementation from the specified super type. Hence a super-invocation can only be used inside an interface definition.
Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
hence they are not supposed to appear in the source program. A value
``$\angl{I}\new{J}$''
is the final result of multiple reduction steps evaluating an
expression. Such value represents an object instance
of $J$ with an annotated static type $I$.

@@

\subsection{Subtyping and Typing Rules}
The subtyping of \MIM{} consists of only a few rules shown at the top of Figure~\ref{fig:typingrules}.
In short, subtyping relations are built from the inheritance in interface
declarations. Subtyping is both reflexive and transitive.

@@

\begin{figure*}[t]
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	% \tsuperinvk \\
	% \tstaticinvk  \\
	\tnew \\
	\tmethod \\
	\tabsmethod \\
	\tintf \\
	\tanno
\end{mathpar}
\label{fig:typingrules}
\saveSpaceFig
\end{figure*}

>>>>

Expressions can be standard constructs such as variables, method
invocation, or object creation. \name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of method invocation: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
implementation for method $m$ should be along the path $I$. 
% Another interesting expression are super-invocations, which enable a method to access an old implementation from the specified super type. Hence a super-invocation can only be used inside an interface definition.
Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
hence they are not supposed to appear in the source program. A value
``$\angl{I}\new{J}$''
is the final result of multiple reduction steps evaluating an
expression. Such value represents an object instance
of $J$ with an annotated static type $I$.

@@

\subsection{Subtyping and Typing Rules}
The subtyping of \MIM{} consists of only a few rules shown at the top of Figure~\ref{fig:typingrules}.
In short, subtyping relations are built from the inheritance in interface
declarations. Subtyping is both symmetric, reflexive and transitive.

@@

\begin{figure}[t]
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\

	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	% \tsuperinvk \\
	% \tstaticinvk  \\
	\tnew \\
	\tmethod \\
	\tabsmethod \\
	\tintf \\
	\tanno
\end{mathpar}
\caption{Typing Rules of \name{}.}
\label{fig:typingrules}
\saveSpaceFig
\end{figure}
